---
title: "DA5020 Homework 4: Strings and Factors"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  # mute messages output
  message = FALSE
)
```

## Preparation

Download US [Farmers Markert Directory](https://www.ams.usda.gov/local-food-directories/farmersmarkets) data from the website of USDA (click on "Export to Excel"). Rename the file as _farmers_market.csv_.

Download the [Know Your Farmer, Know Your Food Projects](https://catalog.data.gov/dataset/know-your-farmer-know-your-food-projects) dataset and name it as _kyfprojects.xls_. Put it into the same folder.


```{r, eval = FALSE}


Read the data:

getwd()
setwd("/Users/amulyashastry/Desktop")


## Warm Up

This dataset stores city and state in different columns, what if you want to
print out city and state in the format "City, State"?

```{r, eval = FALSE}

##Loading Libraries
library("dplyr")
install.packages("stringr")
library("stringr")
install.packages("readxl")
library(readxl)
library(forcats)
library(tidyverse)
```{r, eval = FALSE}


# Question 1

farmers_market<-read.csv("farmers_market.csv",header=T,na.strings = c("",NA))
View(farmers_market)

dull<-mutate(farmers_market,Facebook_new=str_extract_all(Facebook,"[A-Z|0-9][a-z|0-9|A-Z][a-z|A-Z]+-*|^[0-9][0-9]|[a-z]+[:space:]|-|[A-Z]"))
dull<-mutate(dull,Facebook=str_conv())
fb<-dull$Facebook
View(dull)

#[a-z]+[:]+[//][//][a-z]+[.][a-z]+[.][a-z]+[//] - replace facebook.com
str_replace_all(farmers_market$Facebook,"(http|https):[//][//]|(www|ww|m).(f|F)acebook.com[/]",replace="")

#Cleaning Facebook column 
dumb<-mutate(farmers_market, Facebook = str_replace_all(Facebook,"(https|http|www|ww|Facebook|facebook)(|:|.).(com| |)",replace=""))
dur<-mutate(dumb,Facebook = str_replace_all(Facebook, "[//|-]+[0-9][0-9][0-9][0-9][0-9]+",replace=""))

pur<-mutate(dur,Facebook = str_replace_all(Facebook,"[?][a-z]+[=][a-z]+|[&][a-z]+[=][a-z]+[_][a-z]+",replace=""))
bur<-mutate(pur,Facebook= str_replace_all(Facebook,"[//][//][//]pages[/]",replace=""))
bell<-mutate(bur,Facebook= str_replace_all(Facebook,"[//][//][//]",replace=""))
nun<-mutate(bell,Facebook=str_replace_all(Facebook,"#![/]pages[/]",replace=""))
turn<-mutate(nun,Facebook=str_replace_all(Facebook,"[//]",replace=""))

View(timp)
tilt<-mutate(turn,Facebook=str_replace_all(Facebook,"m[.]|pages",replace=""))
tick<-mutate(tilt,Facebook=str_replace_all(Facebook,"[?][a-z]+[_|=][a-z]+[=|&][a-z]+[&|=][a-z|0-9]+[.|_][a-z|0-9]+[=|.][a-z|.][a-z|0-9]+",replace=""))
Final<-mutate(tick,Facebook=str_replace_all(Facebook,"&[a-z]+[=][0-9]+[.][0-9]+[.]+[0-9]+",replace=""))

#Cleaning Twitter column 

twitter<-mutate(Final,Twitter=str_replace_all(Twitter,"@|(https|http):[//]+(www.[a-z]+.com|twitter.com|Twitter.com)[/]",replace=""))
View(twitter3)
twitter2<-mutate(twitter,Twitter=str_replace_all(Twitter,"//(www.twitter.com|twitter.com)",replace=""))
twitter3<-mutate(twitter2,Twitter=str_replace_all(Twitter,"www.twitter.com|twitter.com",replace=""))
Final<-mutate(twitter3,Twitter=str_replace_all(Twitter,"[//]",replace=""))

View(twitter3)
```



```{r, eval = FALSE}
#Question -2

#cleaning street column
street<-mutate(Final,street=str_replace_all(street,"[ ]ST[ ]|Street|ST[.]|St[.]|streets|StreetsStreets|[ ]ST[ ]|ST",replace="St"))

street1<-mutate(street,street=str_replace_all(street,"[ ]and[ ]" ,replace="&"))

bork<-mutate(street1,city=str_replace_all(city,"[,][ ]+[A-Z][A-Z]",replace=""))

#[,][ ]+[A-Z][A-Z]+|[,][ ][A-Z][a-z][.]|[.][ ][A-Z][A-Z]

#Cleaning city column
slim<-mutate(street1,city=str_replace_all(city,"[,][ ][A-Z][A-Z]+|[ ]IN|California|Texas|Idaho|MA|Florida|NM|[ ]ND",replace=""))
Final_city<-mutate(slim,city=str_replace_all(city,"[,][ ]Ma[.]",replace=""))

View(Final_city)

```

#Question 3
```{r, eval = FALSE}
#A tibble
online<-tibble(state=Final_city$State,Facebook=Final_city$Facebook,Twitter=Final_city$Twitter)

#Filtering NA
Final_without_na<-filter(online, !is.na(Facebook),!is.na(Twitter))

#Counting the Facebook accounts 
Final_without_na %>%
  group_by(state) %>%
 count(Facebook) %>%
 add_count(n) ->percent

#Percentage of Facebook account 
percent %>%
  collapse(state) %>%
count(state)-> percent

sum<-sum(percent$nnn)
#percent %>%

percent<-mutate(percent,new = ((nnn/sum)*100))

#Percent of Twitter account
View(percent)

Final_without_na %>%
  group_by(state) %>%
  count(Twitter) %>%
  add_count(n)-> twitter_percent

sum2<-sum(twitter_percent$nn)
twitter_percent<-mutate(twitter_percent,new = ((nn/sum)*100))

View(twitter_percent)
test1

````

```{r, eval = FALSE}

#Question 4
test1<-as_tibble(test1)

#gss_cat %>%
#mutate(partyid=recode(partyid, "Independent" = "ing"))
#mutate(x,fct_recode(x,"a"="A"))
#test1 %>%
 # mutate(MarketName=fct_recode(MarketName, "Caledonia Farmers Market Association - Danville" = "BUM"))


#Shortening the market names 
Final_city$MarketName<-abbreviate(Final_city$MarketName,minlength = 40, use.classes = TRUE,
dot = FALSE, strict = FALSE,
method =  "both.sides", named = TRUE)



Final_city %>% 
  mutate(Location = fct_recode(Location,
                             "PBPL"       = "Private business parking lot",
                             "FSBF"       = "Federal/State government building grounds",
                             "LGBG"       = "Local government building grounds",
                             "COPS"       = "Closed-off public street",
                             "CoWMF"      = "Co-located with wholesale market facility",
                             "EdIn"       = "Educational institution",
                             "FBI"        = "Faith-based institution (e.g., church, mosque, synagogue, temple)",
                             "HcI"        = "Healthcare Institution",
                             "OFF"        = "On a farm from: a barn, a greenhouse, a tent, a stand, etc",
                             "OT"         = "Other" 

)) %>%
  count(Location)-> Plot_tibble


#Plot_tibble<-arrange(Plot_tibble,desc(n))
#Plotting the data

#ggplot(Plot_tibble, aes(Location,n))  +
 # geom_col

ggplot(Plot_tibble, mapping = aes(x = reorder(Plot_tibble$Location, n), y = n)) + 
  geom_bar(stat = "identity") + ylim(0,6500) + labs(title = "Market Locations", subtitle = "32% listed, 68% not listed", x = "Location", y = "Number of Markets")

  
```
 
```{r, eval = FALSE}
#Question 5
getwd()
kyf<-read_xls("kyfprojects.xls",sheet= 1)


kr<-  mutate(kyf,`Program Name`=abbreviate(`Program Name`,minlength=4,use.classes=TRUE))
kr$`Program Name`<-str_match_all(kr$`Program Name`,kr$`Program Abbreviation`)
View(kr)

#Character 0 shows the places where the abbrevations did not match 

isTRUE((kr$`Program Name`==kr$`Program Abbreviation`))

#Sanity check 2 
#checking if the state column is correct
my_states<- state.abb

#for loop to check the 
for (i in kr$State){
if( i == my_states) {
  x =TRUE
}
}

#sanity check 2 



```



## Submission
You need to submit an .Rmd extension file as well as the generated pdf file. Be sure to state all the assumptions and give explanations as comments in the .Rmd file wherever needed to help us assess your submission. Please name the submission file LAST_FirstInitial_1.Rmd for example for John Smith's 1st assignment, the file should be named Smith_J_1.Rmd. 
